How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-06-14 Paper/paper.tex
Updated link to dataset

We ran Kragle on March 2nd 2016 for 24 hours and, in that time, it obtained a little over 250,000 projects. Out of the \nPrograms, we failed to parse and further analyze 2,367 projects due to technical difficulties with the provided JSON files. Kragle, as well as all scraped projects and our analysis files are available.\footnote{\label{repo}\url{https://github.com/ScratchLover42/ICER-Data-Code} \todo{Felienne, what is the new address?} }

>>>>

We ran Kragle on March 2nd 2016 for 24 hours and, in that time, it obtained a little over 250,000 projects. Out of the \nPrograms, we failed to parse and further analyze 2,367 projects due to technical difficulties with the provided JSON files. Kragle, as well as all scraped projects and our analysis files are available.\footnote{\label{repo}\url{https://github.com/TUDelftScratchLab/ScratchDataset}}
